Priors

### 2024-04-10 illustrations/priors.Rmd
Results and prior vis updates

prev_est <- data.frame(
  study = c(
    "Andrews (2014)",
    "Escombe (2008)",
    "Nardell (1991)",
    "Riley (1962)"
  ),
  x = c(0.89, 8.2, 12.5, 1.25),
  y = c(1, 7, 9, 3) / 1e2
) %>%
  mutate(lab = paste0(study, ": ", round(x, 2)))

>>>>

prev_est <- data.frame(
  study = c(
    "Andrews (2014)",
    "Escombe (2008)",
    "Nardell (1991)",
    "Riley (1962)",
    "Dharmadhikari (2012)"
  ),
  x = c(0.89, 8.2, 12.5, 1.25, 138),
  y = c(1, 7, 9, 3, 12) / 1e2
) %>%
  mutate(lab = paste0(study, ": ", round(x, 2)))
